---
title: "Mall Customer Segmentation"
execute: 
  echo: false
---

## Introduction
Customer segmentation is a key marketing strategy that involves dividing a company's customer base into distinct groups of individuals that share similar characteristics. This was sourced from a Kaggle dataset that had basic original mall customer information. The data was filtered and selected to show the relationship between age, gender, Income, and spending score which would possibly become useful for businesses to make the market more effective. The visualizations reveal distinct patterns in age, income, spending behavior, and gender distribution, providing valuable insights for customer segmentation and targeted marketing strategies.

## Data Model

```{r}
#| message: false
#| label: setup

library(tidyverse)
library(scales)
library(plotly)
```
### Age Distributions
The plot allows you to compare the age distributions between male and female customers. For example, you might observe that one gender has a wider age range or a higher concentration of customers within a specific age group.
```{r}
#| message: false
#| warning: false

# Read the CSV file into a data frame and remove rows with missing values
plot1 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na()  # Remove rows with any missing values

# Create a ggplot object for visualizing age distribution by gender
plot1 <- plot1 |>
  ggplot(aes(x = Gender,  # x-axis represents gender
             y = Age,  # y-axis represents age
             fill = Gender)) +  # Fill color based on gender
  geom_boxplot(width = 0.3) +  # Add boxplots with specified width
  geom_violin(alpha = 0.5, width = 0.1) +  # Add violin plots with specified transparency and width
  scale_y_continuous(limits = c(10, 70),  # Set y-axis limits from 10 to 70
                     breaks = seq(10, 70, by = 10)) +  # Define y-axis breaks at intervals of 10
  theme_minimal() +  # Apply a minimalistic theme to the plot
  labs(
    title = "Age Distribution by Gender Among Mall Customers",  # Title of the plot
    subtitle = "Analysis of Age Variations within Gender Groups",  # Subtitle of the plot
    x = "Gender",  # Label for the x-axis
    y = "Age",  # Label for the y-axis
    caption = "Source: Mall Customers Dataset"  # Caption of the plot
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),  # Style the plot title
    plot.subtitle = element_text(size = 12),  # Style the plot subtitle
    axis.title = element_text(size = 12),  # Style the axis titles
    axis.text = element_text(size = 10),  # Style the axis text
    legend.position = "top",  # Position the legend at the top
    legend.title = element_text(size = 12),  # Style the legend title
    legend.text = element_text(size = 10)  # Style the legend text
  )

# Convert the ggplot object into an interactive plotly object
interactive_plot <- ggplotly(plot1)

# Display the interactive plot
interactive_plot
```

