---
title: "Visual Analysis"
execute: 
  echo: false
---

## Central Question
How can we segment mall customers based on their purchasing behaviour to identify what age group and gender has certain spending scores and how do we classify them. 
\n
\n

# Visual Representation
### Age vs Spending scores
this plot represents the base idea which is going to be modified to classify each spender.
```{r}
#| message: false
#| label: setup
# Load necessary libraries
library(tidyverse)
library(scales)
library(plotly)
```

```{r}
#| warning: false
#| message: false


# Read the data from CSV, remove missing values, and select relevant columns
plot5 <- read_csv("Mall_Customers.csv") |>
  drop_na() |>  # Remove rows with any missing values
  select(`Spending Score (1-100)`, Age)  # Select only the 'Spending Score' and 'Age' columns

# Create the ggplot
plot <- ggplot(plot5, aes(x = Age,
                          y = `Spending Score (1-100)`)) +
  geom_point(color = 'blue',
             alpha = 0.6) +  # Add points with blue color and 60% opacity
  geom_density2d(color = 'red') +  # Add red density contours
  geom_smooth(method = 'loess',
              se = FALSE,
              color = 'green') +  # Add a green LOESS smooth line without confidence interval
  scale_y_continuous(limits = c(0, 100),
                     breaks = seq(0, 100, by = 20)) +  # Set y-axis limits and breaks
  labs(
    title = "Age vs. Spending Score",  # Title of the plot
    subtitle = "Analyzing the spending behavior across different age groups",  # Subtitle of the plot
    x = "Age",  # Label for x-axis
    y = "Spending Score (1-100)"  # Label for y-axis
  ) +
  theme_minimal() +  # Apply minimalistic theme
  theme(
    plot.title = element_text(size = 16, face = "bold"),  # Style the plot title
    plot.subtitle = element_text(size = 14),  # Style the plot subtitle
    axis.title = element_text(size = 12),  # Style the axis titles
    axis.text = element_text(size = 10)  # Style the axis text
  )

# Convert the ggplot to an interactive plotly plot
interactive_plot <- ggplotly(plot, tooltip = c("x", "y"))

# Display the interactive plot
interactive_plot
```

### Different types of Spenders
The below graph represents the different types of spenders and their spending scores.
```{r}
#| warning: false
#| message: false

# Read the data from CSV, remove missing values, and create new columns for spender categories
data <- read_csv("Mall_Customers.csv") |>
  drop_na() |>  # Remove rows with any missing values
  mutate(High_Spenders = ifelse(`Spending Score (1-100)` >= 80, 
                                `Spending Score (1-100)`, NA),  # High spenders: Spending Score >= 80
         Low_Spenders = ifelse(`Spending Score (1-100)` <= 40, 
                               `Spending Score (1-100)`, NA),  # Low spenders: Spending Score <= 40
         Medium_Spenders = ifelse(`Spending Score (1-100)` <= 80 & `Spending Score (1-100)` >= 40, 
                                  `Spending Score (1-100)`, NA))  # Medium spenders: Spending Score between 40 and 80

# Create the ggplot
plot6 <- data |>
  ggplot() +
  geom_point(aes(x = Age, y = High_Spenders), 
             color = '#440154FF',  # Dark purple color for high spenders
             size = 1, 
             alpha = 0.8) +  # Semi-transparent points
  geom_point(aes(x = Age, y = Medium_Spenders), 
             color = '#FDE725FF',  # Bright yellow color for medium spenders
             size = 1, 
             alpha = 0.8) +  # Semi-transparent points
  geom_point(aes(x = Age, y = Low_Spenders), 
             color = '#21908CFF',  # Teal color for low spenders
             size = 1, 
             alpha = 0.8) +  # Semi-transparent points
  scale_y_continuous(limits = c(20, 100), 
                     breaks = seq(20, 100, by = 5)) +  # Set y-axis limits and breaks
  labs(
    title = "Different types of Spenders",  # Title of the plot
    subtitle = "High, Medium, and Low Spenders",  # Subtitle of the plot
    caption = "Source: Mall Customers Dataset",  # Caption of the plot
    x = "Age",  # Label for x-axis
    y = "Spending Score (1-100)"  # Label for y-axis
  ) +
  theme_minimal() +  # Apply minimalistic theme
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),  # Style the plot title
    plot.subtitle = element_text(size = 12, face = "italic", hjust = 0.5),  # Style the plot subtitle
    plot.caption = element_text(size = 10, hjust = 1),  # Style the plot caption
    axis.title = element_text(size = 12),  # Style the axis titles
    axis.text = element_text(size = 10)  # Style the axis text
  )

# Convert the ggplot to an interactive plotly plot
interactive_plot <- ggplotly(plot6, tooltip = c("x", "y"))

# Display the interactive plot
interactive_plot
```

### Different types of Spenders based on Gender
The below graph represents different types of spenders but instead of classification of the type of spenders, this graph represents the types of gender that have certain spending scores.
```{r}
#| warning: false
#| message: false

# Read the data from CSV and remove rows with missing values
data <- read_csv("Mall_Customers.csv") |>
  drop_na()  # Remove rows with any missing values

# Create new columns for spender categories based on 'Spending Score (1-100)'
data <- data |>
  mutate(
    High_Spenders = ifelse(`Spending Score (1-100)` >= 80, 
                           `Spending Score (1-100)`, NA),  # High spenders: Spending Score >= 80
    Low_Spenders = ifelse(`Spending Score (1-100)` <= 40, 
                          `Spending Score (1-100)`, NA),  # Low spenders: Spending Score <= 40
    Medium_Spenders = ifelse(`Spending Score (1-100)` < 80 & `Spending Score (1-100)` > 40, 
                             `Spending Score (1-100)`, NA)  # Medium spenders: Spending Score between 40 and 80
  )

# Verify column names to ensure 'Gender' exists in the dataset
if (!"Gender" %in% colnames(data)) {
  stop("Gender column not found in the dataset")  # Stop execution if 'Gender' column is not found
}

# Create the ggplot
plot6 <- data |>
  ggplot() +
  geom_point(aes(x = Age,
                 y = High_Spenders, 
                 color = Gender), 
             size = 1,
             alpha = 0.8) +  # Add points for high spenders
  geom_point(aes(x = Age, y = Medium_Spenders, color = Gender), size = 1, alpha = 0.8) +  # Add points for medium spenders
  geom_point(aes(x = Age, 
                 y = Low_Spenders,
                 color = Gender), 
             size = 1, 
             alpha = 0.8) +  # Add points for low spenders
  scale_y_continuous(limits = c(20, 100),
                     breaks = seq(20, 100, by = 5)) +  # Set y-axis limits and breaks
  labs(
    title = "Spending Scores by Gender",  # Title of the plot
    subtitle = "Spending scores compared to gender",  # Subtitle of the plot
    caption = "Source: Mall Customers Dataset",  # Caption of the plot
    x = "Age",  # Label for x-axis
    y = "Spending Score (1-100)"  # Label for y-axis
  ) +
  theme_minimal() +  # Apply minimalistic theme
  theme(
    plot.title = element_text(size = 16,
                              face = "bold",
                              hjust = 0.5),  # Style the plot title
    plot.subtitle = element_text(size = 12, 
                                 face = "italic",
                                 hjust = 0.5),  # Style the plot subtitle
    plot.caption = element_text(size = 10,
                                hjust = 1),  # Style the plot caption
    axis.title = element_text(size = 12),  # Style the axis titles
    axis.text = element_text(size = 10)  # Style the axis text
  )

# Convert the ggplot to an interactive plotly plot
interactive_plot <- ggplotly(plot6, tooltip = c("x", "y"))

# Display the interactive plot
interactive_plot
```

## Conclusion
These visualizations reveal distinct patterns in age, income, spending behavior, and gender distribution, providing valuable insights for customer segmentation and targeted marketing strategies.

Mall brands, companies, and other businesses benefit when given information about what type of age groups or genders are most common mall shoppers. For example, They most highest spenders are the age groups between age 18 to 40, this could help by encouraging brands to make clothes and other products of fashion that would interest these age groups. Another example could be that the classification of genders and spending scores, this could benefit by allowing brands to make more products that would interest the high spenders of that specific gender and possibly double the profit of those brands
